---
title: ' Clusters & Pneumotypes'
output:
    html_document:
    toc: yes
editor_options: 
    chunk_output_type: console
---
```{r}
source('src/common/load_metadata.r')
source('src/common/load_features.r')
source('src/common/load_lists.r')
source('src/common/nature_theme.r')
source('src/common/graph_features.r')
source('src/common/graph_violin.r')
library(ggridges)
```


# HEATMAPS
## Diagnosis Distribution Heatmap
```{r}
library(viridis)
library(rstatix)

# PURPOSE: plot diagnosis heatmap for pneumotype distribution
plot_heatmap_diagnosis <- function(only_baseline=F, plot_binom = F, plot_chisq = F){
  set.seed(100)
  # STEP1: Prep metadata for plotting
  tab.diagnosis <- permmeta %>% 
    drop_na(cluster_num_amplicon) %>% 
    filter(!Patient_id %in% c(REDACTEDA,REDACTEDB,REDACTEDC)) 
  
  # Optionally, limit to baseline samples only
  if (only_baseline){
    tab.diagnosis <- tab.diagnosis %>% filter(baseline_or_bal == 'Baseline') 
  }
  
  # Calculate summary stats for cleaning (frequency and n)
  tab.diagnosis <- tab.diagnosis %>% 
    dplyr::group_by(Episode_category, cluster_num_amplicon) %>%
    summarise(count=n()) %>% 
    ungroup() %>%
    dplyr::group_by(Episode_category) %>%
    mutate(freq = count/sum(count)) %>%
    mutate(zscale_count = scale(count)) %>% # Not used in plot
    ungroup() %>% 
    mutate(lblcolor = case_when(freq > 0.2 ~ 'black', .default = 'white'))
  
  # STEP2: Distribution statistics
  # Get expected distribution based on npc OR neutral
  expected.p <- tab.diagnosis %>% 
    filter(Episode_category =='NPC') %>%
    group_by(cluster_num_amplicon) %>% 
    summarize(count=sum(count)) %>% #
    mutate(freq = count/sum(count)) %>% 
    pull(freq, cluster_num_amplicon) # Make named list
  # OR use below line if to null
  expected.p <- c(0.25, 0.25, 0.25, 0.25) # NULL distribution
  
  print(c('Expected P: ', expected.p))
  
  label_nudge_y = 0
  
  # Run relevant statistical test
  if (plot_chisq){
    
    print('Executing Chisquare')
    chisq <- tab.diagnosis %>% 
      select(Episode_category, cluster_num_amplicon, count, freq) %>% 
      group_by(Episode_category) %>% 
      select(cluster_num_amplicon, count) %>% 
      summarise(
        data = list(pairwise_chisq_test_against_p(
          count, 
          p=expected.p,
          p.adjust.method = "fdr",
          simulate.p.value = TRUE,  
          B=1e3)
        ),
        cluster_num_amplicon = list(cluster_num_amplicon)) %>%  
      unnest_wider(data) %>%  
      unnest(c(group:p.adj.signif, cluster_num_amplicon)) %>% 
      mutate(p.adj.overall = p.adjust(p, method='fdr')) %>% 
      add_significance(p.col = "p.adj",
                       output.col = 'p.adj.overall.signif',
                       cutpoints = c(0, 0.001, 0.01, 0.05, 1),
                       symbols = c("***", "**", "*", "")
      )
    
    print(chisq, n=Inf)
    
    tab.diagnosis <- tab.diagnosis %>% left_join(chisq)
    
    label_nudge_y = -.12
    
  } else if (plot_binom) {
    
    print('Executing Binomial')
    binom <- tab.diagnosis %>% 
      select(Episode_category, cluster_num_amplicon, count, freq) %>% 
      dplyr::group_by(Episode_category) %>% 
      select(Episode_category, count, cluster_num_amplicon) %>%
      summarise(
        data = list(
          pairwise_binom_test_against_p(
            deframe(select(cur_data_all(), cluster_num_amplicon,count)),
            alternative = "two.sided", #"greater",
            p= expected.p,
            p.adjust.method = "fdr")),
        cluster_num_amplicon = list(cluster_num_amplicon)
      ) %>%  
      unnest_wider(data) %>%  
      unnest(c(group:p.adj.signif,cluster_num_amplicon)) %>% 
      mutate(p.adj.overall = p.adjust(p, method='fdr')) %>% # Column wise or global? Columns are indep.
      add_significance(p.col = "p.adj", 
                       output.col = 'p.adj.signif',
                       cutpoints = c(0, 0.001, 0.01, 0.05, 1),
                       symbols = c("***", "**", "*", ""))
    
    # Print results + combine
    print(binom, n=Inf)
    
    tab.diagnosis <- tab.diagnosis %>% left_join(binom)
    
    label_nudge_y = -.12
  }
  
  # Plot
  p.HeatDistribution <- ggplot(tab.diagnosis, aes(x = Episode_category, 
                                                  y = cluster_num_amplicon,
                                                  fill = freq)) +
    geom_tile(color = "black", linewidth=.2, width=.9) + #.9
    geom_text(aes(label=count, color=lblcolor), size=6/.pt, nudge_y = label_nudge_y) +
    guides(fill = guide_colourbar(label = TRUE,
                                  ticks = FALSE,
                                  title = "Frequency",
                                  frame.linewidth=.2,
                                  frame.colour="black",
                                  ticks.colour = "black",
                                  title.position="top")) +
    theme_nature() +
    scale_fill_viridis() + #limits=c(0,1)) + 
    labs(x="Pneumonia diagnosis", 
         y="Microbiota state") + 
    theme(aspect.ratio = 1.2) +
    scale_color_manual(values=c(white="white", black="black")) +
    guides(color='none')
  
  if (plot_binom | plot_chisq){
    p.HeatDistribution <- p.HeatDistribution + 
      geom_text(aes(label=p.adj.signif, color=lblcolor), size=6/.pt, nudge_y = -label_nudge_y)
  }
  return(p.HeatDistribution)
}

p.HeatDistribution.All <- plot_heatmap_diagnosis(only_baseline = F, plot_binom=T, plot_chisq = F)
p.HeatDistribution.All

p.HeatDistribution <- plot_heatmap_diagnosis(only_baseline = T, plot_binom=T, plot_chisq = F)
p.HeatDistribution

ggsave(filename = 'figures/pneumotypes/04A_DiagnosisHeatAll.pdf',  plot =p.HeatDistribution.All, units='in', width=1.46, height=1.04)
ggsave(filename = 'figures/pneumotypes/04B_DiagnosisHeatBaseline.pdf',  plot = p.HeatDistribution, units='in', width=1.46, height=1.04)



```

## Outcome Distribution Heatmap

```{r}
library(ggh4x)
# PURPOSE: plot clinical outcome heatmap faceted by pneumonia
plot_heatmap_outcome <- function(only_baseline = F, plot_binom = F, plot_chisq = F){
  
  set.seed(100)
  
  # STEP1: Clean metadata for plotting
  success.heat.dt <- permmeta %>%
    drop_na(cluster_num_amplicon) %>%
    filter(!script_id %in% c(REDACTEDA,REDACTEDB,REDACTEDC)) %>% # drop npc that get pneumonia at later tie point
    select(sample_name, cluster_num_amplicon, Episode_category, Episode_is_cured, baseline_or_bal) %>%
    mutate(Episode_is_cured = case_when(Episode_is_cured == 'Not cured' ~ "-", 
                                        Episode_is_cured == 'Indeterminate' ~ "+/-", 
                                        Episode_is_cured == 'Cured' ~ "+", 
                                        .default='npc')) %>% # NON NPC RESOLUTION
    filter(Episode_is_cured != 'npc') %>%
    mutate(Episode_category = factor(Episode_category, levels=c("HAP", "VAP","CAP", "NPC")))
  
  # Optionally, limit to baseline samples only
  if (only_baseline){
    success.heat.dt <- success.heat.dt %>% filter(baseline_or_bal == 'Baseline') 
  }
  
  # Calculate summary stats for cleaning (frequency and n)
  success.heat.dt <- success.heat.dt %>%
    dplyr::group_by(Episode_category, cluster_num_amplicon, Episode_is_cured) %>%
    summarise(count=n()) %>% 
    ungroup() %>%
    complete(Episode_category, cluster_num_amplicon, Episode_is_cured, fill=list(count=0)) %>% # fill any zero values w tidy complete
    dplyr::group_by(Episode_category,cluster_num_amplicon) %>%
    mutate(freq = count/sum(count)) %>%
    ungroup() %>% 
    mutate(zscale_count = scale(freq)) %>%
    mutate(lblcolor = case_when(freq > .6 ~ 'black', .default = 'white')) %>% 
    filter(Episode_category != "NPC") # NON NPC RESOLUTION
  
  # STEP2: Statistics
  # Get baseline outcomes
  expected.p <- success.heat.dt %>% 
    filter(Episode_category =='CAP') %>%
    group_by(Episode_is_cured) %>% 
    summarize(count=sum(count)) %>% #
    mutate(freq = count/sum(count)) %>% 
    arrange(desc(Episode_is_cured)) %>% 
    pull(freq, Episode_is_cured) # Make named list
  # expected.p <- c(0.375,0.625) # CAP distribution
  expected.p <- c(1/3,1/3,1/3) # NULL distribution
  print(c('Expected P: ', expected.p))
  
  
  label_nudge_y = 0
  # return(success.heat.dt)
  if (plot_binom) {
    binom <- success.heat.dt %>%
      filter(Episode_category != 'NPC') %>% # NON NPC RESOLUTION
      select(Episode_category,cluster_num_amplicon, Episode_is_cured, count) %>% 
      dplyr::group_by(Episode_category, cluster_num_amplicon) %>%  #Episode_category, cluster_num_amplicon 
      select(Episode_category, count, cluster_num_amplicon, Episode_is_cured) %>% 
      summarise(
        data = list(
          pairwise_binom_test_against_p(
            deframe(select(cur_data_all(), Episode_is_cured, count)), #cluster_num_amplicon,Episode_is_cured
            alternative = "two.sided", #"greater",
            p = expected.p,
            p.adjust.method = "fdr"
          )),
        Episode_is_cured = list(Episode_is_cured),
        cluster_num_amplicon = list(cluster_num_amplicon)
      ) %>%  
      unnest_wider(data) %>%  
      unnest(c(group:p.adj.signif,Episode_is_cured,cluster_num_amplicon)) %>% 
      mutate(p.adj.overall = p.adjust(p, method='fdr')) %>% 
      add_significance(p.col = "p.adj", # Column wise or global?
                       output.col = 'p.adj.overall.signif',
                       cutpoints = c(0, 0.001, 0.01, 0.05, 1),
                       symbols = c("***", "**", "*", ""))
    # print(binom)
    
    # Combine
    success.heat.dt <- success.heat.dt %>% left_join(binom)
    
    label_nudge_y = -.12
  }
  
  print(success.heat.dt, n=Inf)
  
  # STEP3: PLOT!
  p.success.heat<- success.heat.dt %>% 
    ggplot(., aes(x = cluster_num_amplicon,
                  y = Episode_is_cured,
                  fill = freq)) +
    geom_tile(color = "black", linewidth=.2, width=.9) + #.9
    geom_text(aes(label=count, color = lblcolor), size=6/.pt, nudge_y = label_nudge_y) +
    guides(fill = guide_colourbar(label = TRUE,
                                  ticks = FALSE,
                                  title = "Frequency",
                                  frame.linewidth=.2,
                                  frame.colour="black",
                                  ticks.colour = "black",
                                  title.position="top")) +
    theme_nature()+
    scale_fill_viridis() + 
    labs(x="Microbiota state", 
         y="Pneumonia outcome") + 
    facet_wrap2(~Episode_category, nrow=3, axes='all',remove_labels = 'x') +
    theme(aspect.ratio = .9,
          panel.background = element_blank(),
          strip.background = element_blank(),
          panel.spacing = unit(0, 'pt'),
    ) +
    scale_color_manual(values=c(white="white", black="black")) +
    guides(color='none')
  
  if (plot_binom | plot_chisq){
    p.success.heat <- p.success.heat + 
      geom_text(aes(label=p.adj.overall.signif, color=lblcolor), size=6/.pt, nudge_y = -label_nudge_y)
  }
  
  return(p.success.heat)
  
}

p.success.heat <- plot_heatmap_outcome(F, plot_binom  = T) 
p.success.heat


p.success.heat.baseline <-plot_heatmap_outcome(T, plot_binom = T)
p.success.heat.baseline

ggsave(filename = 'figures/pneumotypes/05A_OutcomeHeatAll.pdf', plot = p.success.heat, units='in', width = 1.53, height=1.82)
ggsave(filename = 'figures/pneumotypes/05B_OutcomeHeatBaseline.pdf', plot = p.success.heat.baseline, units='in', width = 1.53, height=1.82)

```


## Etiology Distribution Heatmap
```{r}
library(viridis)
library(rstatix)

# PURPOSE: plot etiology heatmap for pneumotype distribution
plot_heatmap_etiology <- function(only_baseline=F, plot_binom = F, plot_chisq = F){
  set.seed(100)
  # STEP1: Prep metadata for plotting
  tab.diagnosis <- permmeta %>% 
    drop_na(cluster_num_amplicon) %>% 
    filter(!script_id %in% c(REDACTEDA,REDACTEDB,REDACTEDC)) %>% # drop npc that get pneumonia and lung transplant
    mutate(Episode_etiology = factor(Episode_etiology, levels=c("Bacterial",
                                                                "Viral",
                                                                "Bacterial/viral",
                                                                "Culture-negative",
                                                                "NPC"))) %>% 
    arrange()
  
  
  # Optionally, limit to baseline samples only
  if (only_baseline){
    tab.diagnosis <- tab.diagnosis %>% filter(baseline_or_bal == 'Baseline') 
  }
  
  # Calculate summary stats for cleaning (frequency and n)
  tab.diagnosis <- tab.diagnosis %>% 
    dplyr::group_by(Episode_etiology, cluster_num_amplicon) %>%
    summarise(count=n()) %>% 
    ungroup() %>%
    dplyr::group_by(Episode_etiology) %>%
    mutate(freq = count/sum(count)) %>%
    mutate(zscale_count = scale(count)) %>% # Not used in plot
    ungroup() %>% 
    mutate(lblcolor = case_when(freq > 0.2 ~ 'black', .default = 'white'))
  # print(tab.diagnosis, n=Inf)
  
  # STEP2: Distribution statistics
  # Get expected distribution based on npc OR neutral
  expected.p <- tab.diagnosis %>% 
    filter(Episode_etiology =='NPC') %>%
    group_by(cluster_num_amplicon) %>% 
    summarize(count=sum(count)) %>% #
    mutate(freq = count/sum(count)) %>% 
    pull(freq, cluster_num_amplicon) # Make named list
  # OR use below line if to null
  # expected.p <- c(0.25, 0.25, 0.25, 0.25) # NULL distribution
  
  print(c('Expected P: ', expected.p))
  
  label_nudge_y = 0
  
  # Run relevant statistical test
  if (plot_chisq){
    
    print('Executing Chisquare')
    chisq <- tab.diagnosis %>% 
      select(Episode_etiology, cluster_num_amplicon, count, freq) %>% 
      group_by(Episode_etiology) %>% 
      select(cluster_num_amplicon, count) %>% 
      summarise(
        data = list(pairwise_chisq_test_against_p(
          count, 
          p=expected.p,
          p.adjust.method = "fdr",
          simulate.p.value = TRUE,  
          B=1e3)
        ),
        cluster_num_amplicon = list(cluster_num_amplicon)) %>%  
      unnest_wider(data) %>%  
      unnest(c(group:p.adj.signif, cluster_num_amplicon)) %>% 
      mutate(p.adj.overall = p.adjust(p, method='fdr')) %>% 
      add_significance(p.col = "p.adj",
                       output.col = 'p.adj.overall.signif',
                       cutpoints = c(0, 0.001, 0.01, 0.05, 1),
                       symbols = c("***", "**", "*", "")
      )
    
    print(chisq, n=Inf)
    
    tab.diagnosis <- tab.diagnosis %>% left_join(chisq)
    
    label_nudge_y = -.12
    
  } else if (plot_binom) {
    
    print('Executing Binomial')
    binom <- tab.diagnosis %>% 
      select(Episode_etiology, cluster_num_amplicon, count, freq) %>% 
      dplyr::group_by(Episode_etiology) %>% 
      select(Episode_etiology, count, cluster_num_amplicon) %>%
      summarise(
        data = list(
          pairwise_binom_test_against_p(
            deframe(select(cur_data_all(), cluster_num_amplicon,count)),
            alternative = "greater", #"greater",
            p= expected.p,
            p.adjust.method = "fdr")),
        cluster_num_amplicon = list(cluster_num_amplicon)
      ) %>%  
      unnest_wider(data) %>%  
      unnest(c(group:p.adj.signif,cluster_num_amplicon)) %>% 
      mutate(p.adj.overall = p.adjust(p, method='fdr')) %>% # Column wise or global? Columns are indep.
      add_significance(p.col = "p.adj", 
                       output.col = 'p.adj.signif',
                       cutpoints = c(0, 0.001, 0.01, 0.05, 1),
                       symbols = c("***", "**", "*", ""))
    
    # Print results + combine
    print(binom, n=Inf)
    
    tab.diagnosis <- tab.diagnosis %>% left_join(binom)
    
    label_nudge_y = -.12
  }
  
  # Plot
  p.HeatDistribution <- ggplot(tab.diagnosis, aes(x = Episode_etiology, 
                                                  y = cluster_num_amplicon,
                                                  fill = freq)) +
    geom_tile(color = "black", linewidth=.2, width=.9) + #.9
    geom_text(aes(label=count, color=lblcolor), size=6/.pt, nudge_y = label_nudge_y) +
    guides(fill = guide_colourbar(label = TRUE,
                                  ticks = FALSE,
                                  title = "Frequency",
                                  frame.linewidth=.2,
                                  frame.colour="black",
                                  ticks.colour = "black",
                                  title.position="top")) +
    theme_nature() +
    scale_fill_viridis() + #limits=c(0,1)) + 
    labs(x="Pneumonia diagnosis", 
         y="Microbiota state") + 
    theme(aspect.ratio = 1.2) +
    scale_color_manual(values=c(white="white", black="black")) +
    guides(color='none')
  
  if (plot_binom | plot_chisq){
    p.HeatDistribution <- p.HeatDistribution + 
      geom_text(aes(label=p.adj.signif, color=lblcolor), size=6/.pt, nudge_y = -label_nudge_y)
  }
  return(p.HeatDistribution)
}

p.HeatDistributionEtiology.All <- plot_heatmap_etiology(only_baseline = F, plot_binom=T, plot_chisq = F)
p.HeatDistributionEtiology.All

p.HeatDistributionEtiology <- plot_heatmap_etiology(only_baseline = T, plot_binom=T, plot_chisq = F)
p.HeatDistributionEtiology

ggsave(filename = 'figures/pneumotypes/04A_EtiologyHeatAll.pdf',  plot =p.HeatDistributionEtiology.All, units='in', width=1.46, height=1.04)
ggsave(filename = 'figures/pneumotypes/04B_EtiologyHeatBaseline.pdf',  plot = p.HeatDistributionEtiology, units='in', width=1.46, height=1.04)


```

## EtiologyxOutcome Distribution Heatmap

```{r}
library(ggh4x)
# PURPOSE: plot clinical outcome heatmap faceted by pneumonia
plot_heatmap_etiology <- function(only_baseline = F, plot_binom = F, plot_chisq = F){
  
  set.seed(100)
  
  # STEP1: Clean metadata for plotting
  success.heat.dt <- permmeta %>%
    drop_na(cluster_num_amplicon) %>%
    filter(!script_id %in% c(REDACTEDA,REDACTEDB,REDACTEDC)) %>% # drop npc that get pneumonia and lung transplant
    select(sample_name, cluster_num_amplicon, Episode_etiology, Episode_is_cured, baseline_or_bal) %>%
    mutate(Episode_is_cured = case_when(Episode_is_cured == 'Not cured' ~ "-", 
                                        Episode_is_cured == 'Indeterminate' ~ "+/-", 
                                        Episode_is_cured == 'Cured' ~ "+", 
                                        .default='npc')) %>% # NON NPC RESOLUTION
    filter(Episode_is_cured != 'npc') %>%
    mutate(Episode_etiology = factor(Episode_etiology, levels=c("Bacterial",
                                                                "Viral",
                                                                "Bacterial/viral",
                                                                "Culture-negative",
                                                                "NPC")))
  
  # Optionally, limit to baseline samples only
  if (only_baseline){
    success.heat.dt <- success.heat.dt %>% filter(baseline_or_bal == 'Baseline') 
  }
  
  # Calculate summary stats for cleaning (frequency and n)
  success.heat.dt <- success.heat.dt %>%
    dplyr::group_by(Episode_etiology, cluster_num_amplicon, Episode_is_cured) %>%
    summarise(count=n()) %>% 
    ungroup() %>%
    complete(Episode_etiology, cluster_num_amplicon, Episode_is_cured, fill=list(count=0)) %>% # fill any zero values w tidy complete
    dplyr::group_by(Episode_etiology,cluster_num_amplicon) %>%
    mutate(freq = count/sum(count)) %>%
    ungroup() %>% 
    mutate(zscale_count = scale(freq)) %>%
    mutate(lblcolor = case_when(freq > .6 ~ 'black', .default = 'white')) %>% 
    filter(Episode_etiology != "NPC") # NON NPC RESOLUTION
  
  # STEP2: Statistics
  
  expected.p <- c(1/3,1/3,1/3) # NULL distribution
  print(c('Expected P: ', expected.p))
  
  
  label_nudge_y = 0
  # return(success.heat.dt)
  if (plot_binom) {
    binom <- success.heat.dt %>%
      filter(Episode_etiology != 'NPC') %>% # NON NPC RESOLUTION
      select(Episode_etiology,cluster_num_amplicon, Episode_is_cured, count) %>% 
      dplyr::group_by(Episode_etiology, cluster_num_amplicon) %>%  #Episode_etiology, cluster_num_amplicon 
      select(Episode_etiology, count, cluster_num_amplicon, Episode_is_cured) %>% 
      summarise(
        data = list(
          pairwise_binom_test_against_p(
            deframe(select(cur_data_all(), Episode_is_cured, count)), #cluster_num_amplicon,Episode_is_cured
            alternative = "two.sided", #"greater",
            p = expected.p,
            p.adjust.method = "fdr"
          )),
        Episode_is_cured = list(Episode_is_cured),
        cluster_num_amplicon = list(cluster_num_amplicon)
      ) %>%  
      unnest_wider(data) %>%  
      unnest(c(group:p.adj.signif,Episode_is_cured,cluster_num_amplicon)) %>% 
      mutate(p.adj.overall = p.adjust(p, method='fdr')) %>% 
      add_significance(p.col = "p.adj", # Column wise or global?
                       output.col = 'p.adj.overall.signif',
                       cutpoints = c(0, 0.001, 0.01, 0.05, 1),
                       symbols = c("***", "**", "*", ""))
    # print(binom)
    
    # Combine
    success.heat.dt <- success.heat.dt %>% left_join(binom)
    
    label_nudge_y = -.12
  }
  
  print(success.heat.dt, n=Inf)
  
  # STEP3: PLOT!
  p.success.heat<- success.heat.dt %>% 
    ggplot(., aes(x = cluster_num_amplicon,
                  y = Episode_is_cured,
                  fill = freq)) +
    geom_tile(color = "black", linewidth=.2, width=.9) + #.9
    geom_text(aes(label=count, color = lblcolor), size=6/.pt, nudge_y = label_nudge_y) +
    guides(fill = guide_colourbar(label = TRUE,
                                  ticks = FALSE,
                                  title = "Frequency",
                                  frame.linewidth=.2,
                                  frame.colour="black",
                                  ticks.colour = "black",
                                  title.position="top")) +
    theme_nature()+
    scale_fill_viridis() + 
    labs(x="Microbiota state", 
         y="Pneumonia etiology") + 
    facet_wrap2(~Episode_etiology, nrow=3, axes='all',remove_labels = 'x') +
    theme(aspect.ratio = .9,
          # axis.text.x = element_blank(),
          panel.background = element_blank(),
          strip.background = element_blank(),
          panel.spacing = unit(0, 'pt'),
          # legend.title = element_text(angle = 90), 
          # strip.text = element_text(size=6)
    ) +
    scale_color_manual(values=c(white="white", black="black")) +
    guides(color='none')
  # return(success.heat.dt)
  if (plot_binom | plot_chisq){
    p.success.heat <- p.success.heat + 
      geom_text(aes(label=p.adj.overall.signif, color=lblcolor), size=6/.pt, nudge_y = -label_nudge_y)
  }
  # return(success.heat.dt)
  return(p.success.heat)
  
}

p.success.heat <- plot_heatmap_outcome(F, plot_binom  = T) 
p.success.heat


p.success.heat.baseline <-plot_heatmap_outcome(T, plot_binom = T)
p.success.heat.baseline

ggsave(filename = 'figures/pneumotypes/05A_EtiologyHeatAll.pdf', plot = p.success.heat, units='in', width = 1.53, height=1.82)
ggsave(filename = 'figures/pneumotypes/05B_EtiologyHeatBaseline.pdf', plot = p.success.heat.baseline, units='in', width = 1.53, height=1.82)

```


# FEATURE SIGNATURES

## Exploratory
### Top phyla

```{r}
# write as generic function to use for genus
plot_top_prevalent <- function(my_features, my_column, threshold=0.1){
  
  # get top prev taxa
  top_phyla <- my_features %>% group_by(feature) %>%
    summarize(prevalence = sum(value > 0)/n()) %>%
    arrange(desc(prevalence)) %>%
    filter(prevalence>threshold) %>%
    pluck('feature')
  
  # subset and order
  my_features <- my_features %>%
    group_by(sample_name) %>%
    mutate(value = value/sum(value),
           value = asin(sqrt(value))) %>%
    ungroup() %>%
    filter(feature %in% top_phyla) %>%
    mutate(feature = factor(feature, levels=top_phyla)) %>%
    left_join(permmeta) %>%
    dplyr::rename(my_column = my_column)
  
  # plot
  ggp <- my_features %>%
    drop_na(my_column) %>%
    ggplot(aes(x=feature, y=value, fill=feature)) +
    geom_boxplot() +
    theme_nature() +
    ggh4x::facet_wrap2(~ my_column, axes='all')#,scales ='free_y')
  return(ggp)
}


features_phyla <- get_phylum_taxa() %>% tidy_features()

# Phyla (Exploratory)
plot_top_prevalent(features_phyla, 'cluster_num_amplicon', threshold = 0.2) +
  theme(axis.text.x = element_text(size=3)) +
  rotate_x_text(45)

# Genera (Exploratory)
plot_top_prevalent(mox_feature_list[['AMP [Genus]']] %>% tidy_features(), 'cluster_num_amplicon', threshold = .7) +
  theme(axis.text.x = element_text(size=3)) +
  rotate_x_text(45)

```

### Phyla Density

```{r}
plot_phla_distribution <- function(my_features, my_column, threshold=0.1){
  
  # subset and order
  my_features <- my_features %>%
    group_by(sample_name) %>%
    mutate(value = value/sum(value),
           value = asin(sqrt(value))) %>%
    ungroup() 
  
  # get top prev taxa
  top_phyla <- my_features %>% group_by(feature) %>%
    summarize(prevalence = sum(value > 0)/n()) %>%
    arrange(desc(prevalence)) %>%
    filter(prevalence>threshold) %>%
    pluck('feature')
  
  dput(top_phyla)
  
  my_features <- my_features %>%
    filter(feature %in% top_phyla) %>%
    mutate(feature = factor(feature, levels=top_phyla)) %>%
    left_join(permmeta) %>%
    dplyr::rename(my_column = my_column)
  
  # plot
  ggp <- my_features %>%
    drop_na(my_column) %>%
    ggplot(aes(x=value, y=my_column, fill=my_column)) +
    geom_density_ridges(linewidth=.3, scale = 1.5) +
    theme_nature()+
    labs(x="Abundance", y="Microbiota State") +
    theme(aspect.ratio = 1, 
          legend.position = "none",
          axis.ticks.y = element_blank(),
          # axis.ticks.x = element_blank()
          axis.text.y = element_blank(),
          panel.spacing = unit(6, "pt"),) +     
    ggh4x::facet_wrap2(~ feature,ncol=1, axes='all', remove_labels = 'x') +
    scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']]) 
  # scale_colour_manual(values=darken(mox_color_lists[['Episode_is_cured']], 0.4)) 
  
  return(ggp)
}

# Older version (not ZLR)
phyla_density <- plot_phla_distribution(my_features = features_phyla, my_column = 'cluster_num_amplicon', threshold = .1)
# phyla_density
```
### Shannon Density
```{r}

permmeta <- permmeta %>% left_join(
  vegan::diversity(t(mox_feature_list[['AMP [Genus]']] %>% column_to_rownames('feature')), index='invsimpson') %>% as_tibble(rownames = 'sample_name') %>% dplyr::rename(invsimpson_amp = 'value')
)

library(ggridges)

# As Density Distrib
shannon.density <- permmeta %>% 
  mutate(valuescaled=scale(invsimpson_amp)) %>%
  drop_na(invsimpson_amp) %>% 
  ggplot(., aes(x=invsimpson_amp, 
                y=cluster_num_amplicon, 
                fill=cluster_num_amplicon)) + 
  geom_density_ridges(linewidth=.2, scale = 1) +
  theme_nature()+
  labs(x="Shannon Index", y="Microbiota State") +
  theme(aspect.ratio = 1, 
        legend.position = "none",
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']]) 
shannon.density 
```

## ZLR Phyla + Genera
```{r}
# MOST PREVALENT PHYLA 
features_phyla_tss <- features_phyla %>% 
  wide_features() %>% 
  normalize_feature_table(normalize = T, transform = "none") 

# Top prevalent, should be same as plot printed just before this.
phyla_of_interest <- c("Actinobacteriota", "Firmicutes", "Proteobacteria", "Bacteroidota", "Fusobacteriota", "Patescibacteria") # "Deinococcota", "Chloroflexi", "Campilobacterota", "Planctomycetota", "Verrucomicrobiota"),
phyla_density <- graph_features(features_phyla_tss,
                                feature_array = phyla_of_interest,
                                groups_df = permmeta,
                                feature_col_name = "feature", 
                                group_col_name = 'cluster_num_amplicon', 
                                baseline_group = '1',
                                scale_val=5) +
  xlab(bquote(''~log[2]~"(abund./median abund.)")) +guides(fill='none', color='none')


# MOST ABUNDANT TAXA
get_most_abundant_n(mox_feature_list[["AMP [Genus]"]], 15)
taxa <- top_features
print(length(taxa))

# Undo log2p to make TSS for ZLRs
undo_log2p <- function(feature_list){
    feature_list <- feature_list %>% 
        tidy_features() %>% 
        mutate(value = ((2^value)-1)/100) %>% 
        wide_features()
}
mox_feature_list <- lapply(mox_feature_list, undo_log2p)

genera_density <- graph_features(mox_feature_list[["AMP [Genus]"]],
               taxa, # "Deinococcota", "Chloroflexi", "Campilobacterota", "Planctomycetota", "Verrucomicrobiota"),
               groups_df = permmeta,
               feature_col_name = "feature", 
               group_col_name = 'cluster_num_amplicon',
               baseline_group = '1',
               recode_dash = "-",
               scale_val=5,) +
  xlab(bquote(''~log[2]~"(abund./median abund.)")) +guides(fill='none', color='none')
genera_density
ggsave("figures/pneumotypes/top_30_mean_abundant_feauture.pdf", heigh=6.89, width=2.49)

source('src/common/load_features.r')
drop_samples()
```

# CLUSTER EVIDENCE
## Unifrac Heat
```{r}

# Make Matrix of Weighted UniFrac Dissimilarity and Plot
unif.pairwise<-
  mox_dist_list[['AMP [Genus]']] %>% 
  as.matrix() %>%
  as_tibble(rownames = "Sample.A") %>%
  pivot_longer(cols = 2:last_col(), names_to = "Sample.B", values_to = "UniFrac") %>%
  left_join(mox_cluster_list[['Amplicon']], by = c("Sample.A"="sample_name" )) %>%
  mutate(Cluster.A=case_match(as.numeric(cluster_num), # Change names (not used)
                              1 ~ "1", 2 ~ "2", 3 ~ "3", 4 ~ "4", 5 ~ "5", .default = "D",
                              .ptype = factor(levels = c("1", "2", "3", "4", "5", "D"))), 
         .keep="unused") %>%
  left_join(mox_cluster_list[['Amplicon']], by = c("Sample.B"="sample_name" )) %>%
  mutate(Cluster.B=case_match(as.numeric(cluster_num), # Change names (not used)
                              1 ~ "1", 2 ~ "2", 3 ~ "3", 4 ~ "4", 5 ~ "5", .default = "D",
                              .ptype = factor(levels = c("1", "2", "3", "4", "5", "D"))), 
         .keep="unused") %>%
  select(c(Cluster.A, Cluster.B, UniFrac)) %>% 
  filter(as.integer(Cluster.B) >= as.integer(Cluster.A)) %>% # Lower Triangle and Diagnol
  dplyr::group_by(Cluster.A, Cluster.B) %>%
  summarise(mean = mean(UniFrac)) 


# Plot
p.unif.pairwise <-
  ggplot(unif.pairwise, aes(x = Cluster.A, 
                            y = reorder(Cluster.B, desc(Cluster.B)), 
                            fill= mean)) +
  geom_tile(color = "black", linewidth=.2, width=1) + #.9
  guides(fill = guide_colourbar(label = TRUE,
                                ticks = FALSE,
                                title = "Mean Weighted UniFrac",
                                frame.linewidth=.2,
                                frame.colour="black",
                                ticks.colour = "black",
                                title.position="top")) +
  theme_nature() +
  scale_fill_viridis() + 
  labs(x="Pneumotype", y="Pneumotype") + 
  theme(#axis.text.y = element_blank(), #element_text(hjust = 0),
    #axis.ticks.y = element_blank(),
    aspect.ratio = 1,
    # legend.title = element_text(angle = 90)
  ) +
  rotate_x_text(45)


p.unif.pairwise 
min(unif.pairwise$mean)
max(unif.pairwise$mean)
```


## Consensus Heat

```{r}
# Make plot of Consensus Score 

# Read in + Clean
report <- readRDS('objects/amp/AMP_19_ConsensusClusterReport.rds')
ordered_cluster_names <- names(report[[4]]$consensusClass)
mat.consensus <- report[[4]]$consensusMatrix
row.names(mat.consensus) <- ordered_cluster_names
colnames(mat.consensus) <- ordered_cluster_names
consensus.pairwise <- mat.consensus %>%
  as_tibble(rownames = "Sample.A") %>%
  pivot_longer(cols = 2:last_col(), names_to = "Sample.B", values_to = "Consensus") %>%
  mutate(Sample.A=str_split_i(Sample.A, '-', 1), Sample.A=str_split_i(Sample.A, 'PT', 2), # Make pretty sample names match
         Sample.B=str_split_i(Sample.B, '-', 1), Sample.B=str_split_i(Sample.B, 'PT', 2)) %>%
  left_join(mox_cluster_list[['Amplicon']], by = c("Sample.A"="sample_name" )) %>%
  dplyr::rename(Cluster.A='cluster_num') %>%
  left_join(mox_cluster_list[['Amplicon']], by = c("Sample.B"="sample_name" )) %>%
  dplyr::rename(Cluster.B='cluster_num') %>%
  select(c(Cluster.A, Cluster.B, Consensus)) %>%
  filter(as.integer(Cluster.B) >= as.integer(Cluster.A)) %>% # Lower Triangle and Diagnol
  dplyr::group_by(Cluster.A, Cluster.B) %>%
  summarise(mean = mean(Consensus)) %>%
  ungroup()

# Plot!
p.cons.pairwise <- 
  ggplot(consensus.pairwise, aes(x = Cluster.A, 
                                 y = reorder(Cluster.B, desc(Cluster.B)), 
                                 fill=mean)) +
  geom_tile(color = "black", linewidth=.2, width=1) + #.9
  guides(fill = guide_colourbar(label = TRUE,
                                ticks = FALSE,
                                title = "Mean\nConsensus\nScore",
                                
                                frame.linewidth=.2,
                                frame.colour="black",
                                ticks.colour = "black",
                                title.position="top")) +
  theme_nature()+
  scale_fill_viridis(option="E") + 
  theme(aspect.ratio = 1, 
        legend.position = "right",
  ) +
  labs(x="Pneumotype", y="Pneumotype") 
p.cons.pairwise
```
# VIOLINS
## Abundance & qPCR figures 
```{r}

# QPCR
source('src/common/graph_violin.r')
qPCR_overview <- permmeta %>% 
  drop_na(Quantity.Mean.Log) %>% 
  ggplot(., aes(x=cluster_num_amplicon, y=Quantity.Mean.Log, fill=cluster_num_amplicon)) %>%  #x=outcome
  plot_violin()  %>% 
  plot_statistics(.) +
  scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']])  +
  guides(fill = guide_legend(title = "Pneumotype")) +
  ylab('Log 16S copies/µL') +
  xlab('Pneumotype')#+ theme(aspect.ratio = 1.5)
qPCR_overview

# AMYLASE
amylase <-  permmeta %>% 
  add_clusters() %>% 
  drop_na(cluster_num_amplicon, amylase_bf_log) %>%
  ggplot(., aes(x=cluster_num_amplicon, y=amylase_bf_log, fill=cluster_num_amplicon))  %>% 
  plot_violin(.) %>% plot_statistics(.) +
  scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']])  +
  guides(fill = guide_legend(title = "Pneumotype")) +
  ylab('Log amylase') +
  xlab('Pneumotype') #+ theme(aspect.ratio = 1.5)
amylase
# MDNP
mdnp <-  permmeta %>% add_clusters() %>% 
  drop_na(cluster_num_amplicon) %>%
  ggplot(., aes(x=cluster_num_amplicon, y=dysbiosis_score, fill=cluster_num_amplicon)) %>%   #x=outcome
  plot_violin(.) %>% plot_statistics(.) +
  scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']])  +
  guides(fill = guide_legend(title = "Pneumotype")) +
  # guides(fill = guide_legend(title = "Pneumonia category")) +
  ylab('MDNP score') +
  xlab('Pneumotype')#+ theme(aspect.ratio = 1.5)
mdnp
# NEUTROPHILS
# TODO replace with neutrophil from bodyfluid
neutrophil <-  permmeta %>% 
  drop_na(cluster_num_amplicon, neutrophils_bodyfluid) %>%
  ggplot(., aes(x=cluster_num_amplicon, y=neutrophils_bodyfluid, fill=cluster_num_amplicon))  %>% 
  plot_violin(.) %>% plot_statistics(.) +
  scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']])  +
  guides(fill = guide_legend(title = "Pneumotype")) +
  ylab('Neutrophil level (%)') +
  xlab('Pneumotype')# + theme(aspect.ratio = 1.5)

get_alpha()
# SHANNON
shannon.violin <- permmeta %>%
  drop_na(invsimpson_amp) %>%
  ggplot(., aes(x=cluster_num_amplicon, y=invsimpson_amp, fill=cluster_num_amplicon)) %>% 
  plot_violin(.) %>% 
  plot_statistics(.) +
  scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']])  +
  guides(fill = guide_legend(title = "Pneumotype")) +
  ylab('Inv. Simpson') +
  xlab('Pneumotype') #+ theme(aspect.ratio = 1.5)
shannon.violin

```
# BUBBLES
## Pn. + Overview Bubble
```{r}
source('src/common/graph_bubble_plot.r')
my_bubble <- bubble_plot(mox_dist_list[["AMP [Genus]"]], mox_feature_list[["AMP [Genus]"]], plot_all = T, category_level_plot = 'cluster_num_amplicon') +
  xlab('Pneumotype') +
  ylab(NULL) +
  theme(axis.text.y = element_text(face = 'italic'),
        axis.text.x = element_blank(),
        axis.ticks.x=element_blank()) +
  scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']])
my_bubble
ggsave('figures/pneumotypes/bubble_plot_abundance_mean.pdf', my_bubble, units="in", height=3.32, width=2.75)

# Big Bubbles
library(ghibli)
big_bubble <- bubble_plot(mox_dist_list[["AMP [Genus]"]], mox_feature_list[["AMP [Genus]"]], plot_all = T,filter_top_n = 100, category_level_plot = NULL) +scale_fill_manual(values=mox_color_lists[['cluster_num_amplicon']])
big_bubble <- big_bubble + facet_grid2(~cluster_num_amplicon,space = 'free_x',scales='free_x',shrink = T)
big_bubble
ggsave('figures/pneumotypes/bubble_plot_abundance_facet.pdf', big_bubble, units="in", height=16.57, width=2.49)

```

# NETWORK
## Outcome Network
```{r}
cluster_timeline <- permmeta %>% 
  select(sample_name,script_id,cluster_num_amplicon) %>% 
  drop_na(cluster_num_amplicon) %>% 
  mutate(baseline = case_when(str_ends(sample_name, 'BAL00')~'Baseline',.default='BAL')) %>% 
  arrange(sample_name) %>% 
  group_by(script_id) %>% 
  mutate(order_bal = row_number(sample_name),
         total_bal = n(),
         is_last_bal = case_when(total_bal==order_bal ~ TRUE, .default=FALSE)) %>% 
  mutate(next_bal = lead(cluster_num_amplicon),
         next_bal = case_when(is.na(next_bal) & is_last_bal==T~ 'outcome', .default=next_bal)) %>%  # replace na wth outcome node
  ungroup()


cluster_ntwk <- cluster_timeline %>% 
  group_by(cluster_num_amplicon,next_bal) %>% 
  summarise(n_transition=n()) %>% 
  mutate(sum_cluster=sum(n_transition),
         freq_transiton = round(n_transition/sum(n_transition), 2)) %>% 
  ungroup()

library(igraph)

links <- cluster_ntwk %>% mutate(next_balcolor = next_bal) %>% arrange(desc(next_bal))
nodes <- cluster_ntwk %>% 
  select(cluster_num_amplicon,sum_cluster) %>% 
  unique() %>% 
  add_row(cluster_num_amplicon='outcome', sum_cluster=100) %>% 
  rename(cluster='cluster_num_amplicon') 

colrs <- c('1' = "#F0D77BFF",
           '2' = "#B4DAE5FF",
           '3' = "#AE93BEFF",
           '4' = "#5C5992FF",
           'outcome' = "#999999")
colrs <- c(mox_color_lists[['cluster_num_amplicon']], 'outcome' = "#999999")
# Instantiate graph
net <- graph_from_data_frame(d=links, vertices=nodes, directed=T) 

# Basic igraph visual
l=layout_as_star(net)
plot(net, layout=l,edge.arrow.size=.4,
     vertex.color=colrs,
     vertex.label.color='black',
     vertex.label.cex=.5,
)
# Set edge color
V(net)$size <- scales::rescale(V(net)$sum_cluster, to = c(50, 90))

E(net)$color <- E(net)$next_balcolor

require(tidygraph)
library(ggraph)
library(ghibli)

# Plot ggraph 
pneumotype_network <- ggraph(net,  layout = "stress") +
  geom_edge_fan(aes(label = freq_transiton, color=color), 
                angle_calc = "along",
                # vjust = -.5,
                label_dodge = unit(-1.5, 'mm'),
                label_size = 5/.pt,
                end_cap = circle(.5),
                start_cap = circle(.5),
                arrow = arrow(length = unit(1, 'mm'), type = 'closed'),
                strength=.6
  ) +  scale_edge_colour_manual(values=colrs)+
  geom_edge_loop(aes(label =  as.character(freq_transiton),color=color,strength=.3), 
                 angle_calc = "along", 
                 label_dodge = unit(-1.5, 'mm'),
                 label_size = 5/.pt,
                 end_cap = circle(.5),
                 start_cap = circle(.5),
                 arrow = arrow(length = unit(1, 'mm'), type = 'closed'),
                 check_overlap=T,
  )+
  geom_node_point(aes(fill=name, size=sum_cluster),shape = 21)+
  geom_node_text(aes(label = name), size = 5/.pt) +
  scale_fill_manual(values=colrs) +  
  scale_edge_colour_manual(values=colrs)+
  scale_size_continuous(range = c(4, 8)) +
  
  theme_nature()+
  theme(aspect.ratio = 1,
        axis.line.x = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks=element_blank(),
        # axis.ticks=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        legend.position = 'right') +
  labs(x=NULL,y=NULL)
pneumotype_network
ggsave(filename = 'figures/pneumotypes/figure5_pneumotype_network.pdf',pneumotype_network, units='in', width=3.42, height=2.85)

```
## Only Pneumotype Network
```{r}  
# Simplify
cluster_ntwk <- cluster_ntwk %>% rename(from='cluster_num_amplicon', to='next_bal')

# Get node level information
node_level_dt <- cluster_ntwk %>%  select(from, sum_cluster) %>% unique()

# Instantiate tidygraph and add node attributes
new_graph <- as_tbl_graph(cluster_ntwk) %>% 
  activate(nodes) %>%
  left_join(node_level_dt, by = c("name" = "from")) %>% 
  mutate(sum_cluster = case_when(is.na(sum_cluster)~100, .default=sum_cluster)) %>% # Create pseudovalue for outcome
  filter(name!='outcome') %>% 
  activate(edges) %>%
  mutate(freq_transiton_n=paste0(' ', freq_transiton, ' (n = ', n_transition, ')')) %>%
  
  activate(nodes)



only_pneumotypes_network <- ggraph(new_graph,  layout = "star") +
  geom_edge_parallel2(aes(label = freq_transiton_n, color=as.factor(from),edge_width=freq_transiton), 
                      angle_calc = "along",
                      # vjust = -.5,
                      label_dodge = unit(-.5, 'mm'),
                      label_colour = NA, # makes same color as edge
                      label_size = 2/.pt,
                      end_cap = circle(.2),
                      sep = unit(.5, "mm"),
                      start_cap = circle(.2),
                      arrow = arrow(length = unit(.5, 'mm'), type = 'closed')
  ) +  
  # scale_edge_colour_manual(values=colrs) +
  geom_edge_loop(aes(label =  as.character(freq_transiton_n),
                     color=as.factor(to),
                     strength=.45,span=90, 
                     direction=(ifelse(to==1,x+2.5,x-1))*sign(y+.000001)*sign(x+.000001)*70,# angles to outside
                     edge_width=freq_transiton), 
                 angle_calc = "along", 
                 label_dodge = unit(-.4, 'mm'),
                 label_colour = NA, # makes same color as edge
                 label_size = 2/.pt,
                 end_cap = circle(.1),
                 start_cap = circle(.1),
                 arrow = arrow(length = unit(.5, 'mm'), type = 'closed')
  )+
  geom_node_point(aes(fill=name, size=sum_cluster),shape = 21, stroke=.2) +
  geom_node_text(aes(label = name), size = 2/.pt) +
  scale_fill_manual(values=colrs) +  
  scale_edge_colour_manual(values=colrs)+
  scale_edge_width(range=c(.1,.75)) +
  scale_size_continuous(range = c(1, 2.5)) +
  theme_nature() +
  theme(
    # aspect.ratio = 1,
    axis.line.x = element_blank(),
    axis.line.y = element_blank(),
    axis.ticks=element_blank(),
    # axis.ticks=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    legend.position = 'right',
    legend.margin = margin(1,1,1,1)
  ) +
  labs(x=NULL,y=NULL) +
  guides(edge_color='none', fill='none', edge_width='none', size=guide_legend(title='n (state)')) 
only_pneumotypes_network
ggsave(filename = 'figures/pneumotypes/figure5_only_pneumotype_network.pdf',only_pneumotypes_network, units='in', width=1.42, height=1.05)

```

# MERGING FIGURES
## Long
```{r}
cluster_pcoa <- readRDS('objects/cluster_pcoa.rds') + 
  theme(legend.position = 'right'
        # legend.margin      = margin(1, 1, 1, 1)
  ) + 
  labs(fill='State', shape='Outcome')+guides(shape = "none")


library(patchwork)

{
  #Better
  design <- '
AAB
AAC
DDE
DDF
DDF
'
  
  ## shannon.violin <-shannon.violin+plot_layout(guides = 'collect')
  figure3<- 
    cluster_pcoa + p.cons.pairwise+ shannon.violin + phyla_density+ p.HeatDistribution + p.success.heat + plot_layout(
      design = design,
      guides='collect',
      # heights = c(1, 1,1),
      # widths = c(1, 1,1)
    )  & theme(legend.margin = margin(2,2,2,2))
}
figure3
# ggsave('figures/pneumotypes/figure4_clusters.pdf', figure3, width=6.88, height=4.91, units='in')
# ggsave('figures/pneumotypes/figure4_clusters.pdf', figure3, width= 3.55, height= 4.65, units='in') # 3.58 x 4.76
ggsave('figures/pneumotypes/figure4_clusters.pdf', figure3, width= 3.85, height= 5.30, units='in') # 3.58 x 4.76

```


## Main Plot
```{r}
design <- '
AABDE
AACDE
FGJKE
HILKE
'

## shannon.violin <-shannon.violin+plot_layout(guides = 'collect')
fig.pneumotypes_all <- cluster_pcoa + #A
  p.cons.pairwise +
  shannon.violin +
  phyla_density+ 
  genera_density +
  qPCR_overview + amylase + mdnp+ neutrophil +
  p.HeatDistribution +
  p.success.heat +
  only_pneumotypes_network+
  
  plot_layout(
    design = design, 
    guides = "collect",
    # axis_titles = 'collect',
    widths = c(1, 1,1,1.5,1.5),
    heights=c(1,1,1,1)
  )  + plot_annotation(tag_levels = 'a')#& theme(legend.direction = "vertical", legend.box = "horizontal")
fig.pneumotypes_all
ggsave('figures/pneumotypes/figure4_all_pneumotype_data.pdf', fig.pneumotypes_all, units='in', width=6.88, heigh=4.68)
```
